--- 
title: "Didgeridata"
author: "Adam Santone"
date: '`r Sys.Date()`'
output:
  html_document: default
  pdf_document: default
  word_document: default
description: An MIT pk12 Action Group Lesson for the 2019 MIT STEAM Camp, Hong Kong
documentclass: book
github-repo: asantone/didgeridata
link-citations: yes
bibliography: bibliography.bib
site: bookdown::bookdown_site
biblio-style: apalike
urlcolor: blue
---
```{r include = FALSE}
if(!knitr:::is_html_output())
{
  options("width"=56)
  knitr::opts_chunk$set(tidy.opts=list(width.cutoff=56, indent = 2), tidy = TRUE)
  #knitr::opts_chunk$set(fig.pos = 'H')
  knitr::opts_chunk$set(echo = TRUE, fig.align="center")
}
```

```{r results='hide', message=FALSE, warning=FALSE, echo=FALSE}
#NOTES
#run this command in the RStudio Console to compile: bookdown::render_book("index.Rmd")
#render PDF: bookdown::render_book("index.Rmd", "bookdown::pdf_book")
#render DOC: bookdown::render_book("index.Rmd", "bookdown::word_document2")

#LIBRARIES
#load required libraries
#use additional arguments to suppress warnings and messages
library(knitr)
```


# Introduction {-}

This activity guides groups of students through a brief study of the history and construction of either a didgeridoo, the world's oldest wind instrument, or a paixiao, a chinese pan flute. Students will work with polyvinyl chloride (PVC) pipe and PVC-cutting tools to design and create a playable musical instrument which will be used by students to compose a custom song related to climate data such as atmospheric CO$_{2}$ concentration or global temperature anomalies. In this way, the sonification of climate data will be accomplished with a student musical chorus. The activity will conclude with a group jam session with participants invited to provide percussion for the wind section. An attempt will be made to have expert musicians join the program via teleconference as a guest speaker to provide instruction and background information.


